---
title: "notebook11-Binning data for Tables"
output: html_notebook
---

Load data
```{r}
rm(list=ls(all=TRUE))
load("~/Post-doc/Data/Total Merged Data File (Feb 6 2024).RData")

range(CC.TotalData$turn.anglexysmooth)
head(CC.TotalData)

```

Change factor levels to N, L M H E, etc
```{r}
##CC.TD <- na.omit(CC.TotalData)
data <- CC.TotalData
str(data)
levels(data$Flow.rate) <- c("No Flow","Low Flow (0.6)","Medium Flow (3)", "High Flow (5.9)","Extreme Flow (8.9)")
plot(data$Flow.rate, data$v, xlab = "Flow rate (cm s-1)", ylab = "Velocity (cm s-1)", ylim = c(0, 25))
levels(data$Chlorophyll)
levels(data$Chlorophyll) <- c("No Chlorophyll", "Low Chlorophyll", "Medium Chlorophyll", "High Chlorophyll", "High Chlorophyll","High Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Medium Chlorophyll", "Medium Chlorophyll",  "Medium Chlorophyll",  "Medium Chlorophyll", "Medium Chlorophyll", "Medium Chlorophyll", "Medium Chlorophyll",  "Filament")
plot(data$Chlorophyll, data$v, xlab = "Chlorophyll (mg L-1)", ylab = "Velocity (cm s-1)")

library(ggplot2)
str(data)

par(mar= c(4,4,2,1))
par(mfrow=c(2,2))

######  Chlorophyll
DML$Chem <- "Control"
DMG$Chem <- "Guano"
DMC$Chem <- "Guano+CHL"

DM <- rbind(DML,DMG,DMC)
DM$Chem <- as.factor(DM$Chem)

Medflow <- rbind(DM, LM)
Highflow <- rbind(DH, LH)
str(Medflow)

levels(Highflow$Chem)
levels(Highflow$Chem) <- c("Ambient", "Guano", "Guano+CHL")

Medflow$Chem <- ordered(Medflow$Chem, levels = c("Ambient", "Guano", "Guano+CHL"))


a <- ggplot(data, aes(x = Flow.rate, y = log(v), fill= Chlorophyll))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(legend.key.size = unit(2, "cm"))+
  theme(text = element_text(size = 16))+
  ##stat_summary(fun=mean, geom="line", lty=2, lwd=1, col = "black", aes(group=1)) +
  #stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 #width = 0.25, linetype = "dashed")+
  ##stat_summary(fun=mean, colour="red", geom="point", size = 4) +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme(panel.background = element_rect(fill = "white",
                                colour = "white",
                                linetype = "solid"))+
  theme(axis.line = element_line(linewidth = 0.5, linetype = "solid",
                                   colour = "black"))+
  theme(legend.key = element_rect(fill = "white"))+
  labs(size = "", x = "Flow Rate (cm s-1)", y = "Ground Velocity (logged, cm s-1)", title = "") +
  scale_fill_manual(values=c("white", "gray88", "gray", "gray48", "gray35", "slategray"),name = "Chlorophyll (ug L-1)",
                    labels=c("No Chlorophyll (0)", "Low Chlorophyll (1-5)", "Medium Chlorophyll (6-10)", "High Chlorophyll (11-19)", "Filament"))
  #facet_grid(~ Flow.rate, labeller = label_both, scales = "free_x", space = "free")
a

b <- ggplot(Highflow,aes(x = Chem, y = turn.angle, fill= Chem))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(legend.key.size = unit(2, "cm"))+
  theme(text = element_text(size = 16))+
  ##stat_summary(fun=mean, geom="line", lty=2, lwd=1, col = "black", aes(group=1)) +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = 0.75, linetype = "dashed")+
  ##stat_summary(fun=mean, colour="red", geom="point", size = 4) +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme(panel.background = element_rect(fill = "white",
                                colour = "white",
                                linetype = "solid"))+
  theme(axis.line = element_line(size = 0.5, linetype = "solid",
                                   colour = "black"))+
  theme(legend.key = element_rect(fill = "white"))+
  labs(size = "", x = "Chemical Cue", y = "Turn Angles (degrees)", title = "High Flow (5.9 cm s-1)") +
  scale_fill_manual(values=c("white", "gray", "gray35"),name = "Chemical Cue",
                    labels=c("Ambient", "Guano", "Guano+CHL"))+
  facet_grid(~ Light, labeller = label_both, scales = "free_x", space = "free")
b

c <- ggplot(Highflow,aes(x = Chem, y = pitch.perfect, fill= Chem))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(legend.key.size = unit(2, "cm"))+
  theme(text = element_text(size = 16))+
  ##stat_summary(fun=mean, geom="line", lty=2, lwd=1, col = "black", aes(group=1)) +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = 0.75, linetype = "dashed")+
  ##stat_summary(fun=mean, colour="red", geom="point", size = 4) +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme(panel.background = element_rect(fill = "white",
                                colour = "white",
                                linetype = "solid"))+
  theme(axis.line = element_line(size = 0.5, linetype = "solid",
                                   colour = "black"))+
  theme(legend.key = element_rect(fill = "white"))+
  labs(size = "", x = "Chemical Cue", y = "Vertical Heading (degrees)", title = "High Flow (5.9 cm s-1)") +
  scale_fill_manual(values=c("white", "gray", "gray35"),name = "Chemical Cue",
                    labels=c("Ambient", "Guano", "Guano+CHL"))+
  facet_grid(~ Light, labeller = label_both, scales = "free_x", space = "free")
c


LM$smoothvy <- log10(LM$smooth.vy+3)
LH$smoothvy <- log10(LH$smooth.vy+5.9)

DM$smoothvy <- log10(DM$smooth.vy+3)
DH$smoothvy <- log10(DH$smooth.vy+5.9)

L2 <- rbind(LM,LH)
D2 <- rbind(DM,DH)

d <- ggplot(D2,aes(x=Chlorophyll, y=smoothvy, fill=Chem))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  stat_summary(fun=mean, colour="red", geom="point") +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme_bw()+
  labs(size= "",x = "Chlorophyll", y = "Velocity (cm s-1, logged)", title = "Light Absent") +
  scale_fill_manual(values=c("orange", "green", "white"),name = "Chemicals Present",
                    labels=c("Guano", "Guano+CHL", "None"))+
  facet_grid(~Guano, labeller = label_both, scales = "free_x", space = "free")
d



a
b
c
d

##################


########  Guano

ggplot(data,aes(x=Flow.rate, y=pitch.perfect, fill=Guano))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  labs(size= "",x = "Flow Rate (cm s-1)", y = "Vertical Heading (degrees)", title = "Light") +
  scale_fill_manual(values=c("white", "red"),name = "Guano (3 mg L-1)",
                    labels=c("Guano Absent", "Guano Present"))+
  facet_grid(~Light, scales = "free_x", space = "free")


ggplot(data,aes(x=Flow.rate, y=heading.pi, fill=Guano))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  labs(size= "",x = "Flow Rate (cm s-1)", y = "Horizontal Heading (degrees)", title = "Light") +
  scale_fill_manual(values=c("white", "red"),name = "Guano (3 mg L-1)",
                    labels=c("Guano Absent", "Guano Present"))+
  facet_grid(~Light, scales = "free_x", space = "free")


ggplot(data,aes(x=Flow.rate, y=vel.flow, fill=Guano))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  labs(size= "",x = "Flow Rate (cm s-1)", y = "Velocity in relation to flow (cm s-1)", title = "Light") +
  scale_fill_manual(values=c("white", "red"),name = "Guano (3 mg L-1)",
                    labels=c("Guano Absent", "Guano Present"))+
  facet_grid(~Light, scales = "free_x", space = "free")


ggplot(data,aes(x=Flow.rate, y=vel.turn.angle.smooth, fill=Guano))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  labs(size= "",x = "Flow Rate (cm s-1)", y = "Turn Angles (degrees)", title = "Light") +
  scale_fill_manual(values=c("white", "red"),name = "Guano (3 mg L-1)",
                    labels=c("Guano Absent", "Guano Present"))+
  facet_grid(~Light, scales = "free_x", space = "free")



save.image("~/Post-doc/Data/Total Merged Data File (Sep 14 2023).RData")
```


Aggregated Feeding data for stats
```{r}

DHL$Chem <- "Control"
DHG$Chem <- "Guano"
DHC$Chem <- "Guano+CHL"

DH <- rbind(DHL,DHG,DHC)
levels(DH$Chem)
str(DH)
DH$Chem <- as.factor(DH$Chem)

Medflow <- rbind(DM, LM)
Highflow <- rbind(DH, LH)
str(Medflow)

levels(Medflow$Chem)
levels(Highflow$Chem) <- c("Ambient", "Guano", "Guano+CHL")

Medflow$Chem <- ordered(Medflow$Chem, levels = c("Ambient", "Guano", "Guano+CHL"))

Feeding <- rbind(Medflow, Highflow)
levels(Feeding$Chem)

AGG_Feed <- aggregate(Feeding, by = list(Feeding$D_V_T, Feeding$Guano, Feeding$Light, Feeding$Chem, Feeding$Flow.rate), FUN = mean)
head(AGG_Feed)
AGG_Feed <- AGG_Feed[ -c(6:7, 11:20, 55:57)]
colnames(AGG_Feed) <- c("D_V_T", "Guano", "Light","Chem", "Flow.rate", "X", "Y", "Z", "dx", "dy", "dz", "d", "vx", "vy", "vz", "v", "h.heading", "v.heading", "turn.anglexy", "turn.angleyz", "turn.angle", "vel.turn.angle", "vel", "vel.flow", "trim.X", "xsmooth", "ysmooth", "zsmooth", "smooth.dx", "smooth.dy", "smooth.dz", "smooth.d", "smooth.vx", "smooth.vy", "smooth.vz", "smooth.v", "smooth.h.heading", "heading.pi", "smooth.v.heading", "pitch.perfect", "turn.anglexysmooth", "turn.angleyzsmooth")
head(AGG_Feed)
tail(AGG_Feed)

AGG_Feed
range(AGG_Feed$heading.pi)
##AGG_Feed$turn.anglexysmooth <- AGG_Feed$turn.anglexysmooth/(2*pi)*360

levels(AGG_Feed$Chem)
levels(AGG_Feed$Chem) <- c("Ambient", "Guano", "Guano+CHL")
AGG_Feed$Chem <- ordered(AGG_Feed$Chem, levels = c("Ambient", "Guano", "Guano+CHL"))

library(ggplot2)

a <- ggplot(AGG_Feed,aes(x = Chem, y = turn.anglexysmooth, fill= Chem))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(legend.key.size = unit(2, "cm"))+
  theme(text = element_text(size = 16))+
  ##stat_summary(fun=mean, geom="line", lty=2, lwd=1, col = "black", aes(group=1)) +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = 0.75, linetype = "dashed")+
  ##stat_summary(fun=mean, colour="red", geom="point", size = 4) +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme(panel.background = element_rect(fill = "white",
                                colour = "black",
                                linetype = "solid"))+
  theme(axis.line = element_line(size = 0.5, linetype = "solid",
                                   colour = "black"))+
  theme(legend.key = element_rect(fill = "white"))+
  labs(size = "", x = "Chemical Cue", y = "Vertical heading (degrees)", title = "") +
  scale_fill_manual(values=c("white", "gray", "gray35"),name = "Chemical Cue",
                    labels=c("Ambient", "Guano", "Guano+CHL"))+
  facet_grid(facets = Light ~ Flow.rate, labeller = label_both, scales = "free_x", space = "free")
a

```

aggregate data by factor levels
Find max, min, mean and sd for v and vel.flow

```{r}
str (CC.TotalData)
### aggregate data

agg.data <- aggregate(data, by = list(data$Light, data$Flow.rate, data$Chlorophyll, data$Guano), FUN = mean)
head(agg.data)
agg.data <- agg.data[ -c(5:6, 10:19) ]
head(agg.data)
tail(agg.data)
data$turn.anglexysmooth <- data$turn.anglexysmooth/(2*pi)*360
range(data$vel)
range(data$vel.flow)
range(data$turn.anglexysmooth)
### means, sd, min and max for v and vel flow
library(dplyr)

AGG_Feed %>% group_by(Light, Flow.rate, Chem) %>% summarise_at(vars(heading.pi), lst(min, max, mean, sd))

data %>% group_by(Light, Flow.rate, Chlorophyll, Guano) %>% summarise_at(vars(vel.flow), lst(min, max, mean, sd))

```

Circular stats for angle data
Using Yiping loop for headings

```{r}
######  Chlorophyll
LML$Chem <- "Control"
LMG$Chem <- "Guano"
LMC$Chem <- "Guano+CHL"

######## calculate horizontal heading for each set of conditions e.g., LMG, to get mean, etc
library(dplyr)

full_calculate <- data.frame()
for (dvt in unique(DHC$D_V_T)) {
  data1 <- DHC %>% subset(D_V_T==dvt)
  for (i in 2:nrow(data1)) {
    subdata <- data1[((i-1):i),]
    rel_point_x <- subdata[1,"Z"]
    rel_point_y <- subdata[1,"Y"]
    cal_point_x <- subdata[2,"Z"]
    cal_point_y <- subdata[2,"Y"]
    slope <- (cal_point_y- rel_point_y)/(cal_point_x- rel_point_x)
    angle <- atan(slope)*360/pi
    tmp <- data.frame(D_V_T=dvt,i,rel_point_x,rel_point_y,cal_point_x,cal_point_y,slope,angle)
    full_calculate <- rbind(full_calculate,tmp)
  }
  print(dvt)
}

str(full_calculate)
full_calculate <- na.omit(full_calculate)
full_calculate %>% summarise_at(vars(angle), lst(min, max, mean, median, sd))

```


Total angles
```{r}
### circular stats for angles
range(LML$heading.pi)
library(circular)

range(AGG_Feed$turn.anglexysmooth)
AGG_Feed$turn.anglexysmooth <- AGG_Feed$turn.anglexysmooth/(2*pi)*360

circ.turn <- circular(AGG_Feed$turn.anglexysmooth, type = c("angles"),
          units = c("degrees"),
          template = c("geographics"))

## S3 method for class 'circular'
## as(circ, control.circular=list(), ...) ## NOT WORKING CURRENTLY

## S3 method for class 'circular'
is(circ)

## S3 method for class 'circular'
print(circ, info=TRUE)
range(circ)

## S3 method for class 'circular'
plot(circ, pch = 16, cex = 1, stack = TRUE,
axes = TRUE, start.sep=0, sep = 0.025, shrink = 3.5,   ### larger stack number = more zoomed out
bins = 120, ticks = FALSE, tcl = 0.025, tcl.text = 0.125,
col = NULL, tol = 0.04, uin = NULL,
xlim = c(-1, 1), ylim = c(-1, 1), digits = 2, units = NULL,
template = NULL, zero = NULL, rotation = NULL,
main = NULL, sub=NULL, xlab = "", ylab = "",
control.circle=circle.control())


### calculating mean vector from circular data
mean(circ.turn)

## calculating variance of the vector from circular data
var(circ.turn)

## calculating mean deviation from circular data
meandeviation(circ.turn)

# Compute summary statistics of a random sample of observations. 
summary(circ.turn) 

## ANOVA using circular stats
aov.circular(circ.turn, AGG_Feed$Chem) ## working but unsure

```

Sub-setting factors into separate data sets to calculate mean vectors and dispersion for angle data
```{r}
## Subset each column (each treatment), and assign as circular data
##library(circular)
#####################################################################

   ##  Light On, NO Flow

####################################################################
LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]

LMC <-data[data$Light=="Present",]
LMC <- LMC[LMC$Flow.rate=="Medium Flow",]
LMC <- LMC[LMC$Chlorophyll=="Low Chlorophyll",]
LMC <- LMC[LMC$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]


LHC<-data[data$Light=="Present",]
LHC <- LHC[LHC$Flow.rate=="High Flow",]
LHC <- LHC[LHC$Chlorophyll=="Low Chlorophyll",]
LHC <- LHC[LHC$Guano=="Present",]



################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]

DMC <-data[data$Light=="Absent",]
DMC <- DMC[DMC$Flow.rate=="Medium Flow",]
DMC <- DMC[DMC$Chlorophyll=="Low Chlorophyll",]
DMC <- DMC[DMC$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################
DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]

DHC<-data[data$Light=="Absent",]
DHC <- DHC[DHC$Flow.rate=="High Flow",]
DHC <- DHC[DHC$Chlorophyll=="Low Chlorophyll",]
DHC <- DHC[DHC$Guano=="Present",]

################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]
################################################################



```


```{r}
  ### setting data as circular
##   Lights on

LNN <- circular(LNN$turn.angle, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$turn.angle, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$turn.angle, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$turn.angle, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$turn.angle, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$turn.angle, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$turn.angle, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$turn.angle, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$turn.angle, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$turn.angle, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$turn.angle, units="degrees", template="geographics") #LMN
LML <- circular(LML$turn.angle, units="degrees", template="geographics") #LML
LMM <- circular(LMM$turn.angle, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$turn.angle, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$turn.angle, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$turn.angle, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$turn.angle, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$turn.angle, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$turn.angle, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$turn.angle, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$turn.angle, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$turn.angle, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$turn.angle, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$turn.angle, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$turn.angle, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$turn.angle, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$turn.angle, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$turn.angle, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$turn.angle, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$turn.angle, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$turn.angle, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$turn.angle, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$turn.angle, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$turn.angle, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$turn.angle, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$turn.angle, units="degrees", template="geographics") #DMN
DML <- circular(DML$turn.angle, units="degrees", template="geographics") #DML
DMM <- circular(DMM$turn.angle, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$turn.angle, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$turn.angle, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$turn.angle, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$turn.angle, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$turn.angle, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$turn.angle, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$turn.angle, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$turn.angle, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$turn.angle, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$turn.angle, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$turn.angle, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$turn.angle, units="degrees", template="geographics") #DEG
######################################################################################

#check that the data was subsetted correctly (south & ambient, too if did already)
print(LNN)
print(LNL)
print(LNM)

```

Now that data is subsetted, find the means... and plot circular plot with mean vector

Lights On first...

```{r}
#########################################################################
      ## Lights On No Flow

############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNN, na.rm = TRUE)
meandeviation(LNN, na.rm=TRUE)
summary(LNN, na.rm=TRUE) 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNL, na.rm = TRUE)
meandeviation(LNL, na.rm=TRUE)
summary(LNL, na.rm=TRUE) 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNM, na.rm = TRUE)
meandeviation(LNM, na.rm=TRUE)
summary(LNM, na.rm=TRUE) 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNH, na.rm = TRUE)
meandeviation(LNH, na.rm=TRUE)
summary(LNH, na.rm=TRUE) 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNG, na.rm = TRUE)
meandeviation(LNG, na.rm=TRUE)
summary(LNG, na.rm=TRUE) 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLN, na.rm = TRUE)
meandeviation(LLN, na.rm=TRUE)
summary(LLN, na.rm=TRUE) 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLL, na.rm = TRUE)
meandeviation(LLL, na.rm=TRUE)
summary(LLL, na.rm=TRUE) 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean
var(LLM, na.rm = TRUE)
meandeviation(LLM, na.rm=TRUE)
summary(LLM, na.rm=TRUE) 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean
var(LLH, na.rm = TRUE)
meandeviation(LLH, na.rm=TRUE)
summary(LLH, na.rm=TRUE) 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLG, na.rm = TRUE)
meandeviation(LLG, na.rm=TRUE)
summary(LLG, na.rm=TRUE) 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMN, na.rm = TRUE)
meandeviation(LMN, na.rm=TRUE)
summary(LMN, na.rm=TRUE) 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LML, na.rm = TRUE)
meandeviation(LML, na.rm=TRUE)
summary(LML, na.rm=TRUE)
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMM, na.rm = TRUE)
meandeviation(LMM, na.rm=TRUE)
summary(LMM, na.rm=TRUE)
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMH, na.rm = TRUE)
meandeviation(LMH, na.rm=TRUE)
summary(LMH, na.rm=TRUE)
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMG, na.rm = TRUE)
meandeviation(LMG, na.rm=TRUE)
summary(LMG, na.rm=TRUE)
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHN, na.rm = TRUE)
meandeviation(LHN, na.rm=TRUE)
summary(LHN, na.rm=TRUE)
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHL, na.rm = TRUE)
meandeviation(LHL, na.rm=TRUE)
summary(LHL, na.rm=TRUE)
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHM, na.rm = TRUE)
meandeviation(LHM, na.rm=TRUE)
summary(LHM, na.rm=TRUE)
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHH, na.rm = TRUE)
meandeviation(LHH, na.rm=TRUE)
summary(LHH, na.rm=TRUE)
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHG, na.rm = TRUE)
meandeviation(LHG, na.rm=TRUE)
summary(LHG, na.rm=TRUE)
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEN, na.rm = TRUE)
meandeviation(LEN, na.rm=TRUE)
summary(LEN, na.rm=TRUE)
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEL, na.rm = TRUE)
meandeviation(LEL, na.rm=TRUE)
summary(LEL, na.rm=TRUE)
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEM, na.rm = TRUE)
meandeviation(LEM, na.rm=TRUE)
summary(LEM, na.rm=TRUE)
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEH, na.rm = TRUE)
meandeviation(LEH, na.rm=TRUE)
summary(LEH, na.rm=TRUE)
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEG, na.rm = TRUE)
meandeviation(LEG, na.rm=TRUE)
summary(LEG, na.rm=TRUE)
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################


```
Now for lights off AKA Dark

```{r}
#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DNN, na.rm = TRUE)
meandeviation(DNN, na.rm=TRUE)
summary(DNN, na.rm=TRUE)
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNL, na.rm = TRUE)
meandeviation(DNL, na.rm=TRUE)
summary(DNL, na.rm=TRUE)
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNM, na.rm = TRUE)
meandeviation(DNM, na.rm=TRUE)
summary(DNM, na.rm=TRUE)
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNH, na.rm = TRUE)
meandeviation(DNH, na.rm=TRUE)
summary(DNH, na.rm=TRUE)
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNG, na.rm = TRUE)
meandeviation(DNG, na.rm=TRUE)
summary(DNG, na.rm=TRUE)
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLN, na.rm = TRUE)
meandeviation(DLN, na.rm=TRUE)
summary(DLN, na.rm=TRUE)
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLL, na.rm = TRUE)
meandeviation(DLL, na.rm=TRUE)
summary(DLL, na.rm=TRUE)
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLM, na.rm = TRUE)
meandeviation(DLM, na.rm=TRUE)
summary(DLM, na.rm=TRUE)
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLH, na.rm = TRUE)
meandeviation(DLH, na.rm=TRUE)
summary(DLH, na.rm=TRUE)
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLG, na.rm = TRUE)
meandeviation(DLG, na.rm=TRUE)
summary(DLG, na.rm=TRUE)
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DMN, na.rm = TRUE)
meandeviation(DMN, na.rm=TRUE)
summary(DMN, na.rm=TRUE)
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DML, na.rm = TRUE)
meandeviation(DML, na.rm=TRUE)
summary(DML, na.rm=TRUE)
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DMM, na.rm = TRUE)
meandeviation(DMM, na.rm=TRUE)
summary(DMM, na.rm=TRUE)
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DMH, na.rm = TRUE)
meandeviation(DMH, na.rm=TRUE)
summary(DMH, na.rm=TRUE)
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DMG, na.rm = TRUE)
meandeviation(DMG, na.rm=TRUE)
summary(DMG, na.rm=TRUE)
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHN, na.rm = TRUE)
meandeviation(DHN, na.rm=TRUE)
summary(DHN, na.rm=TRUE)
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHL, na.rm = TRUE)
meandeviation(DHL, na.rm=TRUE)
summary(DHL, na.rm=TRUE)
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHM, na.rm = TRUE)
meandeviation(DHM, na.rm=TRUE)
summary(DHM, na.rm=TRUE)
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHH, na.rm = TRUE)
meandeviation(DHH, na.rm=TRUE)
summary(DHH, na.rm=TRUE)
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHG, na.rm = TRUE)
meandeviation(DHG, na.rm=TRUE)
summary(DHG, na.rm=TRUE)
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEN, na.rm = TRUE)
meandeviation(DEN, na.rm=TRUE)
summary(DEN, na.rm=TRUE)
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEL, na.rm = TRUE)
meandeviation(DEL, na.rm=TRUE)
summary(DEL, na.rm=TRUE)
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEM, na.rm = TRUE)
meandeviation(DEM, na.rm=TRUE)
summary(DEM, na.rm=TRUE)
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEH, na.rm = TRUE)
meandeviation(DEH, na.rm=TRUE)
summary(DEH, na.rm=TRUE)
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEG, na.rm = TRUE)
meandeviation(DEG, na.rm=TRUE)
summary(DEG, na.rm=TRUE)
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEG.mean) #add mean to plot
###########################################################################

```


Test if mean vectors are significantly different...

```{r}
library(circular)
DH$v.heading <- DH$v.heading/(2*pi)*360
range(DH$v.heading)

circDH <- circular(DH$v.heading, type = c("angles"),
          units = c("degrees"),
          template = c("geographics"))

## S3 method for class 'circular'
## as(circ, control.circular=list(), ...) ## NOT WORKING CURRENTLY

## S3 method for class 'circular'
is(circLH)

## S3 method for class 'circular'
print(circLH, info=TRUE)
range(circLH)

## S3 method for class 'circular'
plot(circ, pch = 16, cex = 1, stack = TRUE,
axes = TRUE, start.sep=0, sep = 0.025, shrink = 3.5,   ### larger stack number = more zoomed out
bins = 120, ticks = FALSE, tcl = 0.025, tcl.text = 0.125,
col = NULL, tol = 0.04, uin = NULL,
xlim = c(-1, 1), ylim = c(-1, 1), digits = 2, units = NULL,
template = NULL, zero = NULL, rotation = NULL,
main = NULL, sub=NULL, xlab = "", ylab = "",
control.circle=circle.control())


### calculating mean vector from circular data
mean(circ)

## calculating variance of the vector from circular data
var(circ)

## calculating mean deviation from circular data
meandeviation(circ)

# Compute summary statistics of a random sample of observations. 
summary(circDH) 

## ANOVA using circular stats
aov.circular(circDH, DH$Chem) ## working but unsure


##  A Rayleigh Test is a test for significant unimodal orientation (e.g. Is everyone in the treatment going the same direction?).

rayleigh.test(circLM)  ## if significant shows non-uniformity of direction  (No flow vs extreme flow)
rayleigh.test(circLH)  ## if significant shows non-uniformity of direction

rayleigh.test(circDM)  
rayleigh.test(circDH) 

# Test whether LNN and LEN (etc) orient differently  

##  A Watson Test determines if two groups orientations are significantly different from each other. 
watson.two.test(circLM, circLH, alpha = 0.05)

```

Do it all again for headings.....
```{r}
LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]
################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################

DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]
################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]

```
Run Loop for each set of conditions

Below section has rm for conditions and droplevels for factors at end

```{r}
##########################################################################
##Run Loop for each set of conditions

LLL <- droplevels(LLL)
str(LLL)

library(dplyr)
LLL_calculate <- data.frame()
for (dvt in unique(LLL$D_V_T)) {
  data <- LLL %>% subset(D_V_T==dvt)
  for (i in 2:nrow(data)) {
    subdata <- data[((i-1):i),]
    rel_point_x <- subdata[1,"X"]
    rel_point_y <- subdata[1,"Y"]
    cal_point_x <- subdata[2,"X"]
    cal_point_y <- subdata[2,"Y"]
    slope <- (cal_point_y- rel_point_y)/(cal_point_x- rel_point_x)
    angle <- atan(slope)*360/pi
    tmp <- data.frame(D_V_T=dvt,i,rel_point_x,rel_point_y,cal_point_x,cal_point_y,slope,angle)
    LLL_calculate <- rbind(LLL_calculate,tmp)
  }
  print(dvt)
}

###########################################################################
library(circular)
LNH_calculate.deg <- circular(LNH_calculate$angle, units="degrees", template ="geographics")
LNH_calculate.rad <- LNH_calculate.deg*pi/180   ## converts to radians
LNH_calculate.mean <- mean(LNH_calculate.deg, na.rm = TRUE) #assigns to the 'LNN.mean' object

LNH_calculate.mean  ##*180/pi

plot.circular(DEN_calculate.deg, stack = T, pch = 20, sep = 0.08, shrink = 3.6)  ### larger stack number = more zoomed out
arrows.circular(DEN_calculate.mean-180) #add mean to plot in degrees

############################################################################################

## *180/pi
## *pi/180                     
##head(DEN_calculate)
##DEN_calculate <- DEN_calculate*180/pi   ## converts back to degrees
##mean(DEN_calculate, na.rm = TRUE) #remove NAs from dataset, then find mean 

##-0.01458926*180/pi  ## converts back to degrees

## still in radians below
##var(DEN_calculate, na.rm = TRUE)
##meandeviation(DEN_calculate, na.rm=TRUE)
##summary(DEN_calculate)

####################################################

##  Save mean headings for each set of conditions

####################################################


rm(DEG, DEH, DEM, DHH, DHN, DLG, DLH, DLL, DLM, DMG, DMN, DNG, DNL, LEG, LEH, LHH)
##rm(D, d1, d2, dd, dotprod, doty, dotx, dotz, dx1, dx2, dy1, dy2, dz1, dz2, list2, list3, list4, list5, lth, smoothx1, smoothx2, smoothy1, smoothy2)
##rm(smoothz1, smoothz2, v1, v2, vx1, vx2, vy1, vy2, vz1, vz2, x1, x2, y1, y2, z1, z2)
#####################################################################
LHN <- droplevels(LHN)
str(LHN)

save.image("~/Post-doc/Data/Total Merged Data File (Sep 20 2023).RData")

```

Above section has rm for conditions and droplevels for factors at end

```{r}
##############################################################################
 ### setting data as circular
##   Lights on

head(LNN)

LNN <- circular(LNN$heading.pi, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$heading.pi, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$heading.pi, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$heading.pi, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$heading.pi, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$heading.pi, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$heading.pi, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$heading.pi, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$heading.pi, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$heading.pi, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$heading.pi, units="degrees", template="geographics") #LMN
LML <- circular(LML$heading.pi, units="degrees", template="geographics") #LML
LMM <- circular(LMM$heading.pi, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$heading.pi, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$heading.pi, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$heading.pi, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$heading.pi, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$heading.pi, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$heading.pi, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$heading.pi, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$heading.pi, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$heading.pi, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$heading.pi, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$heading.pi, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$heading.pi, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$heading.pi, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$heading.pi, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$heading.pi, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$heading.pi, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$heading.pi, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$heading.pi, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$heading.pi, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$heading.pi, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$heading.pi, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$heading.pi, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$heading.pi, units="degrees", template="geographics") #DMN
DML <- circular(DML$heading.pi, units="degrees", template="geographics") #DML
DMM <- circular(DMM$heading.pi, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$heading.pi, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$heading.pi, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$heading.pi, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$heading.pi, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$heading.pi, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$heading.pi, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$heading.pi, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$heading.pi, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$heading.pi, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$heading.pi, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$heading.pi, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$heading.pi, units="degrees", template="geographics") #DEG
######################################################################################

```


```{r}
############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DEG.mean) #add mean to plot
###########################################################################
```

and vertical heading......
```{r}
LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]
################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################

DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]
################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]

##########################################################################

##############################################################################
 ### setting data as circular
##   Lights on

head(LNN)

LNN <- circular(LNN$pitch.perfect, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$pitch.perfect, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$pitch.perfect, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$pitch.perfect, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$pitch.perfect, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$pitch.perfect, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$pitch.perfect, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$pitch.perfect, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$pitch.perfect, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$pitch.perfect, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$pitch.perfect, units="degrees", template="geographics") #LMN
LML <- circular(LML$pitch.perfect, units="degrees", template="geographics") #LML
LMM <- circular(LMM$pitch.perfect, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$pitch.perfect, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$pitch.perfect, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$pitch.perfect, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$pitch.perfect, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$pitch.perfect, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$pitch.perfect, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$pitch.perfect, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$pitch.perfect, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$pitch.perfect, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$pitch.perfect, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$pitch.perfect, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$pitch.perfect, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$pitch.perfect, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$pitch.perfect, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$pitch.perfect, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$pitch.perfect, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$pitch.perfect, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$pitch.perfect, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$pitch.perfect, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$pitch.perfect, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$pitch.perfect, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$pitch.perfect, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$pitch.perfect, units="degrees", template="geographics") #DMN
DML <- circular(DML$pitch.perfect, units="degrees", template="geographics") #DML
DMM <- circular(DMM$pitch.perfect, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$pitch.perfect, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$pitch.perfect, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$pitch.perfect, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$pitch.perfect, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$pitch.perfect, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$pitch.perfect, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$pitch.perfect, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$pitch.perfect, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$pitch.perfect, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$pitch.perfect, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$pitch.perfect, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$pitch.perfect, units="degrees", template="geographics") #DEG
######################################################################################

############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DEG.mean) #add mean to plot
###########################################################################


```

```{r}
str(CC.TotalData)

levels(CC.TotalData$D_V)
```

Tests against each other

```{r}   
################################################### Example of testing means of groups against each other
# Ant orientation from Duelli and Wehner (1973) 
# Example used in Batschelet (1981) 


data1 <- list(dahi = circular(DH$v.heading, units="degrees", template="geographics"), dame = circular(DM$v.heading, units="degrees", template="geographics"), lihi = circular(LH$v.heading, units="degrees", template="geographics"), lime = circular(LM$v.heading, units="degrees", template="geographics"))
           
watson.williams.test(data1)


## gives error 
  ##Warning in watson.williams.test.default(x, group) :
  ##Concentration parameters (0.328, 0.231) not equal between groups. The test might not be applicable
##Warning in watson.williams.test.default(x, group) :
  ##Global concentration parameter: 0.314 < 2. The test is probably not applicable

    ## suggests using Wheeler-Watson test instead

watson.wheeler.test(data1)

## gives warning of :
## Warning in watson.wheeler.test.default(x, group) :
  ##There are 75884 ties in the data.
  ##Ties will be broken appart randomly and may influence the result.
  ##Re-run the test several times to check the influence of ties.

          ## after running 4 times: W = (792.65, .78, .8, .7)
          ## all df's = 2
          ## all p-values = 2.2



```

Aggregated Feeding data for stats
```{r}
AGG_Feed <- aggregate(Feeding, by = list(Feeding$D_V_T, Feeding$Guano, Feeding$Light, Feeding$Chem, Feeding$Flow.rate), FUN = mean)
head(AGG_Feed)
AGG_Feed <- AGG_Feed[ -c(6:7, 11:20, 55:57)]
colnames(AGG_Feed) <- c("D_V_T", "Guano", "Light","Chem", "Flow.rate", "X", "Y", "Z", "dx", "dy", "dz", "d", "vx", "vy", "vz", "v", "h.heading", "v.heading", "turn.anglexy", "turn.angleyz", "turn.angle", "vel.turn.angle", "vel", "vel.flow", "trim.X", "xsmooth", "ysmooth", "zsmooth", "smooth.dx", "smooth.dy", "smooth.dz", "smooth.d", "smooth.vx", "smooth.vy", "smooth.vz", "smooth.v", "smooth.h.heading", "heading.pi", "smooth.v.heading", "pitch.perfect", "turn.anglexysmooth", "turn.angleyzsmooth")
head(AGG_Feed)
tail(AGG_Feed)

AGG_Feed
range(AGG_Feed$pitch.perfect)
AGG_Feed$turn.anglexysmooth <- AGG_Feed$turn.anglexysmooth/(2*pi)*360

levels(AGG_Feed$Chem)
levels(AGG_Feed$Chem) <- c("Ambient", "Guano", "Guano+CHL")

AGG_Feed$Chem <- ordered(AGG_Feed$Chem, levels = c("Ambient", "Guano", "Guano+CHL"))

library(ggplot2)

a <- ggplot(AGG_Feed,aes(x = Chem, y = pitch.perfect, fill= Chem))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(legend.key.size = unit(2, "cm"))+
  theme(text = element_text(size = 16))+
  ##stat_summary(fun=mean, geom="line", lty=2, lwd=1, col = "black", aes(group=1)) +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = 0.75, linetype = "dashed")+
  ##stat_summary(fun=mean, colour="red", geom="point", size = 4) +
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  theme(panel.background = element_rect(fill = "white",
                                colour = "black",
                                linetype = "solid"))+
  theme(axis.line = element_line(size = 0.5, linetype = "solid",
                                   colour = "black"))+
  theme(legend.key = element_rect(fill = "white"))+
  labs(size = "", x = "Chemical Cue", y = "Vertical heading (degrees)", title = "") +
  scale_fill_manual(values=c("white", "gray", "gray35"),name = "Chemical Cue",
                    labels=c("Ambient", "Guano", "Guano+CHL"))+
  facet_grid(facets = Light ~ Flow.rate, labeller = label_both, scales = "free_x", space = "free")
a

```


Saving Data.frames as csv files
```{r}
write.csv(Feeding, file = "~/Post-doc/Data/Feeding data Oct 3 2023.csv", row.names = FALSE)

write.csv(CC.TotalData, file = "~/Post-doc/Data/CC.TotalData.Sep.5.2022.csv", row.names = FALSE)

write.csv(data, file = "~/Post-doc/Data/data.Sep.5.2022.csv", row.names = FALSE)

#### Dark conditions save files

write.csv(DEN, file = "~/Post-doc/Data/Conditions Level Data/DEN.csv", row.names = FALSE)
write.csv(DLN, file = "~/Post-doc/Data/Conditions Level Data/DLN.csv", row.names = FALSE)
write.csv(DNH, file = "~/Post-doc/Data/Conditions Level Data/DNH.csv", row.names = FALSE)
write.csv(DNM, file = "~/Post-doc/Data/Conditions Level Data/DNM.csv", row.names = FALSE)
write.csv(DNN, file = "~/Post-doc/Data/Conditions Level Data/DNN.csv", row.names = FALSE)

#### Light conditions save files

write.csv(LNN, file = "~/Post-doc/Data/Conditions Level Data/LNN.csv", row.names = FALSE)
write.csv(LNL, file = "~/Post-doc/Data/Conditions Level Data/LNL.csv", row.names = FALSE)
write.csv(LNM, file = "~/Post-doc/Data/Conditions Level Data/LNM.csv", row.names = FALSE)
write.csv(LNH, file = "~/Post-doc/Data/Conditions Level Data/LNH.csv", row.names = FALSE)
write.csv(LNG, file = "~/Post-doc/Data/Conditions Level Data/LNG.csv", row.names = FALSE)

write.csv(LLN, file = "~/Post-doc/Data/Conditions Level Data/LLN.csv", row.names = FALSE)
write.csv(LLL, file = "~/Post-doc/Data/Conditions Level Data/LLL.csv", row.names = FALSE)
write.csv(LLM, file = "~/Post-doc/Data/Conditions Level Data/LLM.csv", row.names = FALSE)
write.csv(LLG, file = "~/Post-doc/Data/Conditions Level Data/LLG.csv", row.names = FALSE)


write.csv(LMN, file = "~/Post-doc/Data/Conditions Level Data/LMN.csv", row.names = FALSE)
write.csv(LMG, file = "~/Post-doc/Data/Conditions Level Data/LMG.csv", row.names = FALSE)


write.csv(LHN, file = "~/Post-doc/Data/Conditions Level Data/LHN.csv", row.names = FALSE)


write.csv(LEN, file = "~/Post-doc/Data/Conditions Level Data/LEN.csv", row.names = FALSE)


```

Smoothing circular directional data 
```{r}
threshold <- 90
correction <- 180

dat <- read.table("angle_data.txt", header=TRUE)
dat <- ts(dat)

repeat {
    diffs <- dat - lag(dat, k = 1)
    probl <- which(abs(diffs[,2]) > threshold)

    if(length(probl)==0)
        break

    obs.1 <- dat[probl[1], 2]
    obs.2 <- dat[probl[1] + 1, 2]

    dat[probl[1] + 1, 2] <- obs.2 + sign(obs.1 - obs.2) * 180
}





```






