---
title: "notebook11-Binning data for Tables"
output: html_notebook
---

Load data
```{r}
rm(list=ls(all=TRUE))
load("~/Post-doc/Data/Total Merged Data File (Sep 2 2022).RData")

CC.TotalData$turn.anglexy <- atan2(CC.TotalData$X, CC.TotalData$Y)
CC.TotalData$turn.angleyz <- atan2(CC.TotalData$Y, CC.TotalData$Z)


lth <- dim(CC.TotalData)[1]
dx1 <- CC.TotalData$dx[1:(lth-1)]
dx2 <- CC.TotalData$dx[2:lth]
dy1 <- CC.TotalData$dy[1:(lth-1)]
dy2 <- CC.TotalData$dy[2:lth]
dz1 <- CC.TotalData$dz[1:(lth-1)]
dz2 <- CC.TotalData$dz[2:lth]
D <- (dx1*dx2)+(dy1*dy2)+(dz1*dz2)
d1 <- sqrt(dx1^2 + dy1^2 +dz1^2)
d2 <- sqrt(dx2^2 + dy2^2 +dz2^2)

dd <- D/d1/d2
hist(acos(dd)/pi*180)

CC.TotalData$turn.angle <- c(NA, acos(D/d1/d2))/pi*180
```

Change factor levels to N, L M H E, etc
```{r}
##CC.TD <- na.omit(CC.TotalData)
data <- CC.TotalData
str(data)
levels(data$Flow.rate) <- c("No Flow","Low Flow","Medium Flow", "High Flow","Extreme Flow")
plot(data$Flow.rate, data$turn.angle, xlab = "Flow rate (cm s-1)", ylab = "Turn Angles (degrees)", ylim = c(0, 180))

levels(data$Chlorophyll) <- c("No Chlorophyll", "Low Chlorophyll", "Low Chlorophyll", "Medium Chlorophyll", "Medium Chlorophyll",  "Medium Chlorophyll",  "Medium Chlorophyll", "High Chlorophyll")
plot(data$Chlorophyll, data$vel.flow)

library(ggplot2)
ggplot(data,aes(x=Flow.rate, y=pitch.perfect, fill=Chlorophyll))+
  geom_boxplot(notch=F, notchwidth=0.3,outlier.shape=1,outlier.size=2, coef=1.5)+
  theme(axis.text=element_text(color="black"))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.4))+
  theme(panel.grid.minor=element_blank())+
  labs(size= "",x = "Flow Rate (cm s-1)", y = "Pitch (degrees)", title = "Light") +
  scale_fill_manual(values=c("greenyellow", "yellowgreen","lightgreen", "green", "green3", "green4", "darkgreen"),name = "Chlorophyll (mg L-1)",
                    labels=c("No Chlorophyll", "Low Chlorophyll", "Medium Chlorophyll", "High Chlorophyll"))+
  facet_grid(~Light, scales = "free_x", space = "free")



```

aggregate data by factor levels
Find max, min, mean and sd for v and vel.flow
```{r}
str (CC.TotalData)
### aggregate data

agg.data <- aggregate(data, by = list(data$Light, data$Flow.rate, data$Chlorophyll, data$Guano), FUN = mean)
head(agg.data)
agg.data <- agg.data[ -c(5:6, 10:17) ]
head(agg.data)
colnames(agg.data) <- c("Light", "Flow.rate", "Chlorophyll", "Guano", "X", "Y", "Z", "dx", "dy", "dz", "d", "vx", "vy", "vz", "v", "heading", "pitch", "vel.turn.angle", "vel.flow", "trim.X", "xsmooth", "ysmooth", "zsmooth", "smooth.dx", "smooth.dy", "smooth.dz", "smooth.d", "smooth.vx", "smooth.vy", "smooth.vz", "smooth.v", "smooth.heading", "heading.pi", "smooth.pitch", "pitch.perfect", "turn.anglexysmooth",  "turn.angleyzsmooth", "turn.angle.smooth", "vel.turn.angle.smooth", "turn.anglexy", "turn.angleyz", "turn.angle")
head(agg.data)
tail(agg.data)


### means, sd, min and max for v and vel flow

library(dplyr)
data %>% group_by(Light, Flow.rate, Chlorophyll, Guano) %>% summarise_at(vars(v), funs(min, max, mean, sd))

data %>% group_by(Light, Flow.rate, Chlorophyll, Guano) %>% summarise_at(vars(vel.flow), funs(min, max, mean, sd))

```

Circular stats for angle data
Total angles
```{r}
### circular stats for angles
range(data$turn.angle)
library(circular)

circ <- circular(data$turn.angle, type = c("angles"),
          units = c("degrees"),
          template = c("geographics"))

## S3 method for class 'circular'
## as(circ, control.circular=list(), ...) ## NOT WORKING CURRENTLY

## S3 method for class 'circular'
is(circ)

## S3 method for class 'circular'
print(circ, info=TRUE)


## S3 method for class 'circular'
plot(circ, pch = 16, cex = 1, stack = TRUE,
axes = TRUE, start.sep=0, sep = 0.025, shrink = 3.5,   ### larger stack number = more zoomed out
bins = 120, ticks = FALSE, tcl = 0.025, tcl.text = 0.125,
col = NULL, tol = 0.04, uin = NULL,
xlim = c(-1, 1), ylim = c(-1, 1), digits = 2, units = NULL,
template = NULL, zero = NULL, rotation = NULL,
main = NULL, sub=NULL, xlab = "", ylab = "",
control.circle=circle.control())


### calculating mean vector from circular data
mean(circ)

## calculating variance of the vector from circular data
var(circ)

## calculating mean deviation from circular data
meandeviation(circ)

# Compute summary statistics of a random sample of observations. 
summary(circ) 

## ANOVA using circular stats
aov.circular(circ, CC.TotalData$Light) ## working but unsure

```

Sub-setting factors into separate data sets to calculate mean vectors and dispersion for angle data
```{r}
## Subset each column (each treatment), and assign as circular data
library(circular)
#####################################################################

   ##  Light On, NO Flow

####################################################################

LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]
################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################

DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]
################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]
################################################################
  ### setting data as circular
##   Lights on

LNN <- circular(LNN$turn.angle, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$turn.angle, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$turn.angle, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$turn.angle, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$turn.angle, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$turn.angle, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$turn.angle, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$turn.angle, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$turn.angle, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$turn.angle, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$turn.angle, units="degrees", template="geographics") #LMN
LML <- circular(LML$turn.angle, units="degrees", template="geographics") #LML
LMM <- circular(LMM$turn.angle, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$turn.angle, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$turn.angle, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$turn.angle, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$turn.angle, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$turn.angle, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$turn.angle, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$turn.angle, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$turn.angle, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$turn.angle, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$turn.angle, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$turn.angle, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$turn.angle, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$turn.angle, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$turn.angle, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$turn.angle, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$turn.angle, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$turn.angle, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$turn.angle, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$turn.angle, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$turn.angle, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$turn.angle, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$turn.angle, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$turn.angle, units="degrees", template="geographics") #DMN
DML <- circular(DML$turn.angle, units="degrees", template="geographics") #DML
DMM <- circular(DMM$turn.angle, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$turn.angle, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$turn.angle, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$turn.angle, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$turn.angle, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$turn.angle, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$turn.angle, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$turn.angle, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$turn.angle, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$turn.angle, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$turn.angle, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$turn.angle, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$turn.angle, units="degrees", template="geographics") #DEG
######################################################################################

#check that the data was subsetted correctly (south & ambient, too if did already)
print(LNN)
print(LNL)
print(LNM)

```

Now that data is subsetted, find the means... and plot circular plot with mean vector

Lights On first...

```{r}
#########################################################################
      ## Lights On No Flow

############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNN, na.rm = TRUE)
meandeviation(LNN, na.rm=TRUE)
summary(LNN, na.rm=TRUE) 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNL, na.rm = TRUE)
meandeviation(LNL, na.rm=TRUE)
summary(LNL, na.rm=TRUE) 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNM, na.rm = TRUE)
meandeviation(LNM, na.rm=TRUE)
summary(LNM, na.rm=TRUE) 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNH, na.rm = TRUE)
meandeviation(LNH, na.rm=TRUE)
summary(LNH, na.rm=TRUE) 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LNG, na.rm = TRUE)
meandeviation(LNG, na.rm=TRUE)
summary(LNG, na.rm=TRUE) 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLN, na.rm = TRUE)
meandeviation(LLN, na.rm=TRUE)
summary(LLN, na.rm=TRUE) 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLL, na.rm = TRUE)
meandeviation(LLL, na.rm=TRUE)
summary(LLL, na.rm=TRUE) 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean
var(LLM, na.rm = TRUE)
meandeviation(LLM, na.rm=TRUE)
summary(LLM, na.rm=TRUE) 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean
var(LLH, na.rm = TRUE)
meandeviation(LLH, na.rm=TRUE)
summary(LLH, na.rm=TRUE) 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LLG, na.rm = TRUE)
meandeviation(LLG, na.rm=TRUE)
summary(LLG, na.rm=TRUE) 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMN, na.rm = TRUE)
meandeviation(LMN, na.rm=TRUE)
summary(LMN, na.rm=TRUE) 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LML, na.rm = TRUE)
meandeviation(LML, na.rm=TRUE)
summary(LML, na.rm=TRUE)
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMM, na.rm = TRUE)
meandeviation(LMM, na.rm=TRUE)
summary(LMM, na.rm=TRUE)
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMH, na.rm = TRUE)
meandeviation(LMH, na.rm=TRUE)
summary(LMH, na.rm=TRUE)
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LMG, na.rm = TRUE)
meandeviation(LMG, na.rm=TRUE)
summary(LMG, na.rm=TRUE)
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHN, na.rm = TRUE)
meandeviation(LHN, na.rm=TRUE)
summary(LHN, na.rm=TRUE)
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHL, na.rm = TRUE)
meandeviation(LHL, na.rm=TRUE)
summary(LHL, na.rm=TRUE)
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHM, na.rm = TRUE)
meandeviation(LHM, na.rm=TRUE)
summary(LHM, na.rm=TRUE)
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHH, na.rm = TRUE)
meandeviation(LHH, na.rm=TRUE)
summary(LHH, na.rm=TRUE)
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LHG, na.rm = TRUE)
meandeviation(LHG, na.rm=TRUE)
summary(LHG, na.rm=TRUE)
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEN, na.rm = TRUE)
meandeviation(LEN, na.rm=TRUE)
summary(LEN, na.rm=TRUE)
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEL, na.rm = TRUE)
meandeviation(LEL, na.rm=TRUE)
summary(LEL, na.rm=TRUE)
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEM, na.rm = TRUE)
meandeviation(LEM, na.rm=TRUE)
summary(LEM, na.rm=TRUE)
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEH, na.rm = TRUE)
meandeviation(LEH, na.rm=TRUE)
summary(LEH, na.rm=TRUE)
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(LEG, na.rm = TRUE)
meandeviation(LEG, na.rm=TRUE)
summary(LEG, na.rm=TRUE)
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################


```
Now for lights off AKA Dark

```{r}
#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DNN, na.rm = TRUE)
meandeviation(DNN, na.rm=TRUE)
summary(DNN, na.rm=TRUE)
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNL, na.rm = TRUE)
meandeviation(DNL, na.rm=TRUE)
summary(DNL, na.rm=TRUE)
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNM, na.rm = TRUE)
meandeviation(DNM, na.rm=TRUE)
summary(DNM, na.rm=TRUE)
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNH, na.rm = TRUE)
meandeviation(DNH, na.rm=TRUE)
summary(DNH, na.rm=TRUE)
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DNG, na.rm = TRUE)
meandeviation(DNG, na.rm=TRUE)
summary(DNG, na.rm=TRUE)
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLN, na.rm = TRUE)
meandeviation(DLN, na.rm=TRUE)
summary(DLN, na.rm=TRUE)
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLL, na.rm = TRUE)
meandeviation(DLL, na.rm=TRUE)
summary(DLL, na.rm=TRUE)
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLM, na.rm = TRUE)
meandeviation(DLM, na.rm=TRUE)
summary(DLM, na.rm=TRUE)
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLH, na.rm = TRUE)
meandeviation(DLH, na.rm=TRUE)
summary(DLH, na.rm=TRUE)
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DLG, na.rm = TRUE)
meandeviation(DLG, na.rm=TRUE)
summary(DLG, na.rm=TRUE)
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DMN, na.rm = TRUE)
meandeviation(DMN, na.rm=TRUE)
summary(DMN, na.rm=TRUE)
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DML, na.rm = TRUE)
meandeviation(DML, na.rm=TRUE)
summary(DML, na.rm=TRUE)
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DMM, na.rm = TRUE)
meandeviation(DMM, na.rm=TRUE)
summary(DMM, na.rm=TRUE)
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DMH, na.rm = TRUE)
meandeviation(DMH, na.rm=TRUE)
summary(DMH, na.rm=TRUE)
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean
var(DMG, na.rm = TRUE)
meandeviation(DMG, na.rm=TRUE)
summary(DMG, na.rm=TRUE)
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHN, na.rm = TRUE)
meandeviation(DHN, na.rm=TRUE)
summary(DHN, na.rm=TRUE)
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHL, na.rm = TRUE)
meandeviation(DHL, na.rm=TRUE)
summary(DHL, na.rm=TRUE)
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHM, na.rm = TRUE)
meandeviation(DHM, na.rm=TRUE)
summary(DHM, na.rm=TRUE)
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHH, na.rm = TRUE)
meandeviation(DHH, na.rm=TRUE)
summary(DHH, na.rm=TRUE)
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DHG, na.rm = TRUE)
meandeviation(DHG, na.rm=TRUE)
summary(DHG, na.rm=TRUE)
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEN, na.rm = TRUE)
meandeviation(DEN, na.rm=TRUE)
summary(DEN, na.rm=TRUE)
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEL, na.rm = TRUE)
meandeviation(DEL, na.rm=TRUE)
summary(DEL, na.rm=TRUE)
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEM, na.rm = TRUE)
meandeviation(DEM, na.rm=TRUE)
summary(DEM, na.rm=TRUE)
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEH, na.rm = TRUE)
meandeviation(DEH, na.rm=TRUE)
summary(DEH, na.rm=TRUE)
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
var(DEG, na.rm = TRUE)
meandeviation(DEG, na.rm=TRUE)
summary(DEG, na.rm=TRUE)
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEG.mean) #add mean to plot
###########################################################################

```


Test if mean vectors are significantly different...

```{r}


##  A Rayleigh Test is a test for significant unimodal orientation (e.g. Is everyone in the treatment going the same direction?).

rayleigh.test(LNN)  ## if significant shows non-uniformity of direction  (No flow vs extreme flow)
rayleigh.test(LEN)  ## if significant shows non-uniformity of direction

# Test whether LNN and LEN (etc) orient differently  

##  A Watson Test determines if two groups’ orientations are significantly different from each other. 
watson.two.test(LNN, LEN)

```

Do it all again for headings.....
```{r}
LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]
################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################

DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]
################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]

```
Run Loop for each set of conditions

Below section has rm for conditions and droplevels for factors at end

```{r}
##########################################################################
##Run Loop for each set of conditions

library(dplyr)
DEN_calculate <- data.frame()
for (dvt in unique(DEN$D_V_T)) {
  data <- DEN %>% subset(D_V_T==dvt)
  for (i in 2:nrow(data)) {
    subdata <- data[((i-1):i),]
    rel_point_x <- subdata[1,"X"]
    rel_point_y <- subdata[1,"Y"]
    cal_point_x <- subdata[2,"X"]
    cal_point_y <- subdata[2,"Y"]
    slope <- (cal_point_y- rel_point_y)/(cal_point_x- rel_point_x)
    angle <- atan(slope)*360/pi
    tmp <- data.frame(D_V_T=dvt,i,rel_point_x,rel_point_y,cal_point_x,cal_point_y,slope,angle)
    DEN_calculate <- rbind(DEN_calculate,tmp)
  }
  print(dvt)
}


###########################################################################
library(circular)
DEN_calculate <- circular(DEN_calculate$angle, units="degrees", template ="geographics")
DEN_calculate <- DEN_calculate*pi/180   ## converts to radians
DEN_calculate.mean <- mean(DEN_calculate*180/pi, na.rm = TRUE) #assigns to the 'LNN.mean' object



                         
head(LEN_calculate)
LNL_calculate <- LNL_calculate*pi/180   ## converts to radians
mean(LNN_calculate, na.rm = TRUE) #remove NAs from dataset, then find mean 

0.0316*180/pi  ## converts back to degrees

## still in radians below
var(LEN_calculate, na.rm = TRUE)
meandeviation(LEN_calculate, na.rm=TRUE)
summary(LEN_calculate)

LNL_calculate.mean <- mean(LNL_calculate*180/pi, na.rm = TRUE) #assigns to the 'LNN.mean' object
plot.circular(LEN_calculate, stack = T, pch = 20, sep = 0.08, shrink = 3.6)  ### larger stack number = more zoomed out
arrows.circular(LEN_calculate.mean) #add mean to plot



####################################################

##  Save mean headings for each set of conditions

####################################################


rm(DEG, DEH, DEL, DEM, DHG, DHH, DHL, DHM, DHN, DLG, DLH, DLL, DLM, DMG, DMH, DML, DMM, DMN, DNG, DNL, LEG, LEH, LEL, LEM, LHG, LHH, LHL, LHM, LLH, LMH, LML, LMM)
##rm(D, d1, d2, dd, dotprod, doty, dotx, dotz, dx1, dx2, dy1, dy2, dz1, dz2, list2, list3, list4, list5, lth, smoothx1, smoothx2, smoothy1, smoothy2)
##rm(smoothz1, smoothz2, v1, v2, vx1, vx2, vy1, vy2, vz1, vz2, x1, x2, y1, y2, z1, z2)

LNN <- droplevels(LNN)
str(LNN)

```

Above section has rm for conditions and droplevels for factors at end

```{r}
##############################################################################
 ### setting data as circular
##   Lights on

head(LNN)

LNN <- circular(LNN$heading.pi, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$heading.pi, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$heading.pi, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$heading.pi, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$heading.pi, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$heading.pi, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$heading.pi, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$heading.pi, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$heading.pi, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$heading.pi, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$heading.pi, units="degrees", template="geographics") #LMN
LML <- circular(LML$heading.pi, units="degrees", template="geographics") #LML
LMM <- circular(LMM$heading.pi, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$heading.pi, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$heading.pi, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$heading.pi, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$heading.pi, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$heading.pi, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$heading.pi, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$heading.pi, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$heading.pi, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$heading.pi, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$heading.pi, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$heading.pi, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$heading.pi, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$heading.pi, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$heading.pi, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$heading.pi, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$heading.pi, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$heading.pi, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$heading.pi, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$heading.pi, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$heading.pi, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$heading.pi, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$heading.pi, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$heading.pi, units="degrees", template="geographics") #DMN
DML <- circular(DML$heading.pi, units="degrees", template="geographics") #DML
DMM <- circular(DMM$heading.pi, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$heading.pi, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$heading.pi, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$heading.pi, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$heading.pi, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$heading.pi, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$heading.pi, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$heading.pi, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$heading.pi, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$heading.pi, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$heading.pi, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$heading.pi, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$heading.pi, units="degrees", template="geographics") #DEG
######################################################################################

```


```{r}
############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DEG.mean) #add mean to plot
###########################################################################
```

and pitch......
```{r}
LNN<-data[data$Light=="Present",]
LNN <- LNN[LNN$Flow.rate=="No Flow",]
LNN <- LNN[LNN$Chlorophyll=="No Chlorophyll",]
LNN <- LNN[LNN$Guano=="Absent",]

LNL<-data[data$Light=="Present",]
LNL <- LNL[LNL$Flow.rate=="No Flow",]
LNL <- LNL[LNL$Chlorophyll=="Low Chlorophyll",]
LNL <- LNL[LNL$Guano=="Absent",]

LNM<-data[data$Light=="Present",]
LNM <- LNM[LNM$Flow.rate=="No Flow",]
LNM <- LNM[LNM$Chlorophyll=="Medium Chlorophyll",]
LNM <- LNM[LNM$Guano=="Absent",]

LNH<-data[data$Light=="Present",]
LNH <- LNH[LNH$Flow.rate=="No Flow",]
LNH <- LNH[LNH$Chlorophyll=="High Chlorophyll",]
LNH <- LNH[LNH$Guano=="Absent",]

LNG<-data[data$Light=="Present",]
LNG <- LNG[LNG$Flow.rate=="No Flow",]
LNG <- LNG[LNG$Chlorophyll=="No Chlorophyll",]
LNG <- LNG[LNG$Guano=="Present",]
##############################################################

##    Lights On, Low Flow

###############################################################

LLN<-data[data$Light=="Present",]
LLN <- LLN[LLN$Flow.rate=="Low Flow",]
LLN <- LLN[LLN$Chlorophyll=="No Chlorophyll",]
LLN <- LLN[LLN$Guano=="Absent",]

LLL<-data[data$Light=="Present",]
LLL <- LLL[LLL$Flow.rate=="Low Flow",]
LLL <- LLL[LLL$Chlorophyll=="Low Chlorophyll",]
LLL <- LLL[LLL$Guano=="Absent",]

LLM<-data[data$Light=="Present",]
LLM <- LLM[LLM$Flow.rate=="Low Flow",]
LLM <- LLM[LLM$Chlorophyll=="Medium Chlorophyll",]
LLM <- LLM[LLM$Guano=="Absent",]

LLH<-data[data$Light=="Present",]
LLH <- LLH[LLH$Flow.rate=="Low Flow",]
LLH <- LLH[LLH$Chlorophyll=="High Chlorophyll",]
LLH <- LLH[LLH$Guano=="Absent",]

LLG<-data[data$Light=="Present",]
LLG <- LLG[LLG$Flow.rate=="Low Flow",]
LLG <- LLG[LLG$Chlorophyll=="No Chlorophyll",]
LLG <- LLG[LLG$Guano=="Present",]
#####################################################################

##    Light On, Medium Flow

######################################################################

LMN<-data[data$Light=="Present",]
LMN <- LMN[LMN$Flow.rate=="Medium Flow",]
LMN <- LMN[LMN$Chlorophyll=="No Chlorophyll",]
LMN <- LMN[LMN$Guano=="Absent",]

LML<-data[data$Light=="Present",]
LML <- LML[LML$Flow.rate=="Medium Flow",]
LML <- LML[LML$Chlorophyll=="Low Chlorophyll",]
LML <- LML[LML$Guano=="Absent",]

LMM<-data[data$Light=="Present",]
LMM <- LMM[LMM$Flow.rate=="Medium Flow",]
LMM <- LMM[LMM$Chlorophyll=="Medium Chlorophyll",]
LMM <- LMM[LMM$Guano=="Absent",]

LMH<-data[data$Light=="Present",]
LMH <- LMH[LMH$Flow.rate=="Medium Flow",]
LMH <- LMH[LMH$Chlorophyll=="High Chlorophyll",]
LMH <- LMH[LMH$Guano=="Absent",]

LMG<-data[data$Light=="Present",]
LMG <- LMG[LMG$Flow.rate=="Medium Flow",]
LMG <- LMG[LMG$Chlorophyll=="No Chlorophyll",]
LMG <- LMG[LMG$Guano=="Present",]
################################################################

###    Light On, High Flow

####################################################################

LHN<-data[data$Light=="Present",]
LHN <- LHN[LHN$Flow.rate=="High Flow",]
LHN <- LHN[LHN$Chlorophyll=="No Chlorophyll",]
LHN <- LHN[LHN$Guano=="Absent",]

LHL<-data[data$Light=="Present",]
LHL <- LHL[LHL$Flow.rate=="High Flow",]
LHL <- LHL[LHL$Chlorophyll=="Low Chlorophyll",]
LHL <- LHL[LHL$Guano=="Absent",]

LHM<-data[data$Light=="Present",]
LHM <- LHM[LHM$Flow.rate=="High Flow",]
LHM <- LHM[LHM$Chlorophyll=="Medium Chlorophyll",]
LHM <- LHM[LHM$Guano=="Absent",]

LHH<-data[data$Light=="Present",]
LHH <- LHH[LHH$Flow.rate=="High Flow",]
LHH <- LHH[LHH$Chlorophyll=="High Chlorophyll",]
LHH <- LHH[LHH$Guano=="Absent",]

LHG<-data[data$Light=="Present",]
LHG <- LHG[LHG$Flow.rate=="High Flow",]
LHG <- LHG[LHG$Chlorophyll=="No Chlorophyll",]
LHG <- LHG[LHG$Guano=="Present",]
################################################################


###    Light On, Extreme Flow

####################################################################

LEN<-data[data$Light=="Present",]
LEN <- LEN[LEN$Flow.rate=="Extreme Flow",]
LEN <- LEN[LEN$Chlorophyll=="No Chlorophyll",]
LEN <- LEN[LEN$Guano=="Absent",]

LEL<-data[data$Light=="Present",]
LEL <- LEL[LEL$Flow.rate=="Extreme Flow",]
LEL <- LEL[LEL$Chlorophyll=="Low Chlorophyll",]
LEL <- LEL[LEL$Guano=="Absent",]

LEM<-data[data$Light=="Present",]
LEM <- LEM[LEM$Flow.rate=="Extreme Flow",]
LEM <- LEM[LEM$Chlorophyll=="Medium Chlorophyll",]
LEM <- LEM[LEM$Guano=="Absent",]

LEH<-data[data$Light=="Present",]
LEH <- LEH[LEH$Flow.rate=="Extreme Flow",]
LEH <- LEH[LEH$Chlorophyll=="High Chlorophyll",]
LEH <- LEH[LEH$Guano=="Absent",]

LEG<-data[data$Light=="Present",]
LEG <- LEG[LEG$Flow.rate=="Extreme Flow",]
LEG <- LEG[LEG$Chlorophyll=="No Chlorophyll",]
LEG <- LEG[LEG$Guano=="Present",]
################################################################

#####################################################################

   ##  Light Off, NO Flow

####################################################################

DNN<-data[data$Light=="Absent",]
DNN <- DNN[DNN$Flow.rate=="No Flow",]
DNN <- DNN[DNN$Chlorophyll=="No Chlorophyll",]
DNN <- DNN[DNN$Guano=="Absent",]

DNL<-data[data$Light=="Absent",]
DNL <- DNL[DNL$Flow.rate=="No Flow",]
DNL <- DNL[DNL$Chlorophyll=="Low Chlorophyll",]
DNL <- DNL[DNL$Guano=="Absent",]

DNM<-data[data$Light=="Absent",]
DNM <- DNM[DNM$Flow.rate=="No Flow",]
DNM <- DNM[DNM$Chlorophyll=="Medium Chlorophyll",]
DNM <- DNM[DNM$Guano=="Absent",]

DNH <-data[data$Light=="Absent",]
DNH <- DNH[DNH$Flow.rate=="No Flow",]
DNH <- DNH[DNH$Chlorophyll=="High Chlorophyll",]
DNH <- DNH[DNH$Guano=="Absent",]

DNG<-data[data$Light=="Absent",]
DNG <- DNG[DNG$Flow.rate=="No Flow",]
DNG <- DNG[DNG$Chlorophyll=="No Chlorophyll",]
DNG <- DNG[DNG$Guano=="Present",]
##############################################################

##    Lights Off, Low Flow

###############################################################

DLN <-data[data$Light=="Absent",]
DLN <- DLN[DLN$Flow.rate=="Low Flow",]
DLN <- DLN[DLN$Chlorophyll=="No Chlorophyll",]
DLN <- DLN[DLN$Guano=="Absent",]

DLL <-data[data$Light=="Absent",]
DLL <- DLL[DLL$Flow.rate=="Low Flow",]
DLL <- DLL[DLL$Chlorophyll=="Low Chlorophyll",]
DLL <- DLL[DLL$Guano=="Absent",]

DLM <-data[data$Light=="Absent",]
DLM <- DLM[DLM$Flow.rate=="Low Flow",]
DLM <- DLM[DLM$Chlorophyll=="Medium Chlorophyll",]
DLM <- DLM[DLM$Guano=="Absent",]

DLH <-data[data$Light=="Absent",]
DLH <- DLH[DLH$Flow.rate=="Low Flow",]
DLH <- DLH[DLH$Chlorophyll=="High Chlorophyll",]
DLH <- DLH[DLH$Guano=="Absent",]

DLG <-data[data$Light=="Absent",]
DLG <- DLG[DLG$Flow.rate=="Low Flow",]
DLG <- DLG[DLG$Chlorophyll=="No Chlorophyll",]
DLG <- DLG[DLG$Guano=="Present",]
#####################################################################

##    Light Off, Medium Flow

######################################################################

DMN <-data[data$Light=="Absent",]
DMN <- DMN[DMN$Flow.rate=="Medium Flow",]
DMN <- DMN[DMN$Chlorophyll=="No Chlorophyll",]
DMN <- DMN[DMN$Guano=="Absent",]

DML <-data[data$Light=="Absent",]
DML <- DML[DML$Flow.rate=="Medium Flow",]
DML <- DML[DML$Chlorophyll=="Low Chlorophyll",]
DML <- DML[DML$Guano=="Absent",]

DMM <-data[data$Light=="Absent",]
DMM <- DMM[DMM$Flow.rate=="Medium Flow",]
DMM <- DMM[DMM$Chlorophyll=="Medium Chlorophyll",]
DMM <- DMM[DMM$Guano=="Absent",]

DMH <-data[data$Light=="Absent",]
DMH <- DMH[DMH$Flow.rate=="Medium Flow",]
DMH <- DMH[DMH$Chlorophyll=="High Chlorophyll",]
DMH <- DMH[DMH$Guano=="Absent",]

DMG <-data[data$Light=="Absent",]
DMG <- DMG[DMG$Flow.rate=="Medium Flow",]
DMG <- DMG[DMG$Chlorophyll=="No Chlorophyll",]
DMG <- DMG[DMG$Guano=="Present",]
################################################################

###    Light Off, High Flow

####################################################################

DHN<-data[data$Light=="Absent",]
DHN <- DHN[DHN$Flow.rate=="High Flow",]
DHN <- DHN[DHN$Chlorophyll=="No Chlorophyll",]
DHN <- DHN[DHN$Guano=="Absent",]

DHL<-data[data$Light=="Absent",]
DHL <- DHL[DHL$Flow.rate=="High Flow",]
DHL <- DHL[DHL$Chlorophyll=="Low Chlorophyll",]
DHL <- DHL[DHL$Guano=="Absent",]

DHM<-data[data$Light=="Absent",]
DHM <- DHM[DHM$Flow.rate=="High Flow",]
DHM <- DHM[DHM$Chlorophyll=="Medium Chlorophyll",]
DHM <- DHM[DHM$Guano=="Absent",]

DHH<-data[data$Light=="Absent",]
DHH <- DHH[DHH$Flow.rate=="High Flow",]
DHH <- DHH[DHH$Chlorophyll=="High Chlorophyll",]
DHH <- DHH[DHH$Guano=="Absent",]

DHG<-data[data$Light=="Absent",]
DHG <- DHG[DHG$Flow.rate=="High Flow",]
DHG <- DHG[DHG$Chlorophyll=="No Chlorophyll",]
DHG <- DHG[DHG$Guano=="Present",]
################################################################


###    Light Off, Extreme Flow

####################################################################

DEN<-data[data$Light=="Absent",]
DEN <- DEN[DEN$Flow.rate=="Extreme Flow",]
DEN <- DEN[DEN$Chlorophyll=="No Chlorophyll",]
DEN <- DEN[DEN$Guano=="Absent",]

DEL<-data[data$Light=="Absent",]
DEL <- DEL[DEL$Flow.rate=="Extreme Flow",]
DEL <- DEL[DEL$Chlorophyll=="Low Chlorophyll",]
DEL <- DEL[DEL$Guano=="Absent",]

DEM<-data[data$Light=="Absent",]
DEM <- DEM[DEM$Flow.rate=="Extreme Flow",]
DEM <- DEM[DEM$Chlorophyll=="Medium Chlorophyll",]
DEM <- DEM[DEM$Guano=="Absent",]

DEH<-data[data$Light=="Absent",]
DEH <- DEH[DEH$Flow.rate=="Extreme Flow",]
DEH <- DEH[DEH$Chlorophyll=="High Chlorophyll",]
DEH <- DEH[DEH$Guano=="Absent",]

DEG<-data[data$Light=="Absent",]
DEG <- DEG[DEG$Flow.rate=="Extreme Flow",]
DEG <- DEG[DEG$Chlorophyll=="No Chlorophyll",]
DEG <- DEG[DEG$Guano=="Present",]

##########################################################################

##############################################################################
 ### setting data as circular
##   Lights on

head(LNN)

LNN <- circular(LNN$pitch.perfect, units="degrees", template="geographics") #assign LNN subset to "LNN" variable
LNL <- circular(LNL$pitch.perfect, units="degrees", template="geographics") #LNL
LNM <- circular(LNM$pitch.perfect, units="degrees", template="geographics") #LNM
LNH <- circular(LNH$pitch.perfect, units="degrees", template="geographics") #LNH
LNG <- circular(LNG$pitch.perfect, units="degrees", template="geographics") #LNG

LLN <- circular(LLN$pitch.perfect, units="degrees", template="geographics") #LLN
LLL <- circular(LLL$pitch.perfect, units="degrees", template="geographics") #LLL
LLM <- circular(LLM$pitch.perfect, units="degrees", template="geographics") #LLM
LLH <- circular(LLH$pitch.perfect, units="degrees", template="geographics") #LLH
LLG <- circular(LLG$pitch.perfect, units="degrees", template="geographics") #LLG

LMN <- circular(LMN$pitch.perfect, units="degrees", template="geographics") #LMN
LML <- circular(LML$pitch.perfect, units="degrees", template="geographics") #LML
LMM <- circular(LMM$pitch.perfect, units="degrees", template="geographics") #LMM
LMH <- circular(LMH$pitch.perfect, units="degrees", template="geographics") #LMH
LMG <- circular(LMG$pitch.perfect, units="degrees", template="geographics") #LMG

LHN <- circular(LHN$pitch.perfect, units="degrees", template="geographics") #LHN
LHL <- circular(LHL$pitch.perfect, units="degrees", template="geographics") #LHL
LHM <- circular(LHM$pitch.perfect, units="degrees", template="geographics") #LHM
LHH <- circular(LHH$pitch.perfect, units="degrees", template="geographics") #LHH
LHG <- circular(LHG$pitch.perfect, units="degrees", template="geographics") #LHG

LEN <- circular(LEN$pitch.perfect, units="degrees", template="geographics") #LEN
LEL <- circular(LEL$pitch.perfect, units="degrees", template="geographics") #LEL
LEM <- circular(LEM$pitch.perfect, units="degrees", template="geographics") #LEM
LEH <- circular(LEH$pitch.perfect, units="degrees", template="geographics") #LEH
LEG <- circular(LEG$pitch.perfect, units="degrees", template="geographics") #LEG

############  Lights Off

DNN <- circular(DNN$pitch.perfect, units="degrees", template="geographics") #DNN
DNL <- circular(DNL$pitch.perfect, units="degrees", template="geographics") #DNL
DNM <- circular(DNM$pitch.perfect, units="degrees", template="geographics") #DNM
DNH <- circular(DNH$pitch.perfect, units="degrees", template="geographics") #DNH
DNG <- circular(DNG$pitch.perfect, units="degrees", template="geographics") #DNG

DLN <- circular(DLN$pitch.perfect, units="degrees", template="geographics") #DLN
DLL <- circular(DLL$pitch.perfect, units="degrees", template="geographics") #DLL
DLM <- circular(DLM$pitch.perfect, units="degrees", template="geographics") #DLM
DLH <- circular(DLH$pitch.perfect, units="degrees", template="geographics") #DLH
DLG <- circular(DLG$pitch.perfect, units="degrees", template="geographics") #DLG

DMN <- circular(DMN$pitch.perfect, units="degrees", template="geographics") #DMN
DML <- circular(DML$pitch.perfect, units="degrees", template="geographics") #DML
DMM <- circular(DMM$pitch.perfect, units="degrees", template="geographics") #DMM
DMH <- circular(DMH$pitch.perfect, units="degrees", template="geographics") #DMH
DMG <- circular(DMG$pitch.perfect, units="degrees", template="geographics") #DMG

DHN <- circular(DHN$pitch.perfect, units="degrees", template="geographics") #DHN
DHL <- circular(DHL$pitch.perfect, units="degrees", template="geographics") #DHL
DHM <- circular(DHM$pitch.perfect, units="degrees", template="geographics") #DHM
DHH <- circular(DHH$pitch.perfect, units="degrees", template="geographics") #DHH
DHG <- circular(DHG$pitch.perfect, units="degrees", template="geographics") #DHG

DEN <- circular(DEN$pitch.perfect, units="degrees", template="geographics") #DEN
DEL <- circular(DEL$pitch.perfect, units="degrees", template="geographics") #DEL
DEM <- circular(DEM$pitch.perfect, units="degrees", template="geographics") #DEM
DEH <- circular(DEH$pitch.perfect, units="degrees", template="geographics") #DEH
DEG <- circular(DEG$pitch.perfect, units="degrees", template="geographics") #DEG
######################################################################################

############################################################################
mean(LNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNN.mean <- mean(LNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(LNN.mean) #add mean to plot
###########################################################################

mean(LNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNL.mean <- mean(LNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNL.mean) #add mean to plot
###########################################################################

mean(LNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNM.mean <- mean(LNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNM.mean) #add mean to plot
###########################################################################

mean(LNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNH.mean <- mean(LNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNH.mean) #add mean to plot
###########################################################################

mean(LNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LNG.mean <- mean(LNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Low Flow

############################################################################
mean(LLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLN.mean <- mean(LLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLN.mean) #add mean to plot
###########################################################################

mean(LLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLL.mean <- mean(LLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLL.mean) #add mean to plot
###########################################################################

mean(LLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLM.mean <- mean(LLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLM.mean) #add mean to plot
###########################################################################

mean(LLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLH.mean <- mean(LLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLH.mean) #add mean to plot
###########################################################################

mean(LLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LLG.mean <- mean(LLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(LMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMN.mean <- mean(LMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMN.mean) #add mean to plot
###########################################################################

mean(LML, na.rm = TRUE) #remove NAs from dataset, then find mean 
LML.mean <- mean(LML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LML.mean) #add mean to plot
###########################################################################

mean(LMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMM.mean <- mean(LMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMM.mean) #add mean to plot
###########################################################################

mean(LMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMH.mean <- mean(LMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMH.mean) #add mean to plot
###########################################################################

mean(LMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LMG.mean <- mean(LMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On High Flow

############################################################################
mean(LHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHN.mean <- mean(LHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHN.mean) #add mean to plot
###########################################################################

mean(LHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHL.mean <- mean(LHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHL.mean) #add mean to plot
###########################################################################

mean(LHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHM.mean <- mean(LHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHM.mean) #add mean to plot
###########################################################################

mean(LHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHH.mean <- mean(LHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHH.mean) #add mean to plot
###########################################################################

mean(LHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LHG.mean <- mean(LHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LHG.mean) #add mean to plot
###########################################################################



#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(LEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEN.mean <- mean(LEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEN.mean) #add mean to plot
###########################################################################

mean(LEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEL.mean <- mean(LEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEL.mean) #add mean to plot
###########################################################################

mean(LEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEM.mean <- mean(LEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEM.mean) #add mean to plot
###########################################################################

mean(LEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEH.mean <- mean(LEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEH.mean) #add mean to plot
###########################################################################

mean(LEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
LEG.mean <- mean(LEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(LEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(LEG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off No Flow

############################################################################
mean(DNN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNN.mean <- mean(DNN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DNN.mean) #add mean to plot
###########################################################################

mean(DNL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNL.mean <- mean(DNL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNL.mean) #add mean to plot
###########################################################################

mean(DNM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNM.mean <- mean(DNM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNM.mean) #add mean to plot
###########################################################################

mean(DNH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNH.mean <- mean(DNH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNH.mean) #add mean to plot
###########################################################################

mean(DNG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DNG.mean <- mean(DNG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DNG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DNG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights Off Low Flow

############################################################################
mean(DLN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLN.mean <- mean(DLN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLN.mean) #add mean to plot
###########################################################################

mean(DLL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLL.mean <- mean(DLL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLL.mean) #add mean to plot
###########################################################################

mean(DLM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLM.mean <- mean(DLM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLM.mean) #add mean to plot
###########################################################################

mean(DLH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLH.mean <- mean(DLH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLH.mean) #add mean to plot
###########################################################################

mean(DLG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DLG.mean <- mean(DLG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DLG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DLG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights On Medium Flow

############################################################################
mean(DMN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMN.mean <- mean(DMN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMN.mean) #add mean to plot
###########################################################################

mean(DML, na.rm = TRUE) #remove NAs from dataset, then find mean 
DML.mean <- mean(DML, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DML, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DML.mean) #add mean to plot
###########################################################################

mean(DMM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMM.mean <- mean(DMM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMM.mean) #add mean to plot
###########################################################################

mean(DMH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMH.mean <- mean(DMH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMH.mean) #add mean to plot
###########################################################################

mean(DMG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DMG.mean <- mean(DMG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DMG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DMG.mean) #add mean to plot
###########################################################################


#########################################################################
      ## Lights Off High Flow

############################################################################
mean(DHN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHN.mean <- mean(DHN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHN.mean) #add mean to plot
###########################################################################

mean(DHL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHL.mean <- mean(DHL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHL.mean) #add mean to plot
###########################################################################

mean(DHM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHM.mean <- mean(DHM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHM.mean) #add mean to plot
###########################################################################

mean(DHH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHH.mean <- mean(DHH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHH.mean) #add mean to plot
###########################################################################

mean(DHG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DHG.mean <- mean(DHG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DHG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DHG.mean) #add mean to plot
###########################################################################

#########################################################################
      ## Lights On Extreme Flow

############################################################################
mean(DEN, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEN.mean <- mean(DEN, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEN, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEN.mean) #add mean to plot
###########################################################################

mean(DEL, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEL.mean <- mean(DEL, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEL, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEL.mean) #add mean to plot
###########################################################################

mean(DEM, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEM.mean <- mean(DEM, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEM, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEM.mean) #add mean to plot
###########################################################################

mean(DEH, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEH.mean <- mean(DEH, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEH, stack = T, pch = 20, sep = 0.08, shrink = 1.6)
arrows.circular(DEH.mean) #add mean to plot
###########################################################################

mean(DEG, na.rm = TRUE) #remove NAs from dataset, then find mean 
DEG.mean <- mean(DEG, na.rm = TRUE) #assigns to the 'LNN.mean' object

plot.circular(DEG, stack = T, pch = 20, sep = 0.08, shrink = 1.6)  ### larger stack number = more zoomed out
arrows.circular(DEG.mean) #add mean to plot
###########################################################################


```

```{r}
str(CC.TotalData)

levels(CC.TotalData$D_V)
```

Tests against each other

```{r}   
################################################### Example of testing means of groups against each other
# Ant orientation from Duelli and Wehner (1973) 
# Example used in Batschelet (1981) 
data1 <- list( exp = circular(rep(c(-20,-10, 0), c(1,7,2)), units="degrees", template="geographics"), control = circular(rep(c(-10, 0, 10, 20), c(3,3,3,1)), units="degrees", template="geographics")
          ) 
watson.williams.test(data1)




```

Saving Data.frames as csv files
```{r}
write.csv(agg.data, file = "~/Post-doc/Data/agg.data.Sep.5.2022.csv", row.names = FALSE)

write.csv(CC.TotalData, file = "~/Post-doc/Data/CC.TotalData.Sep.5.2022.csv", row.names = FALSE)

write.csv(data, file = "~/Post-doc/Data/data.Sep.5.2022.csv", row.names = FALSE)

#### Dark conditions save files

write.csv(DEN, file = "~/Post-doc/Data/Conditions Level Data/DEN.csv", row.names = FALSE)
write.csv(DLN, file = "~/Post-doc/Data/Conditions Level Data/DLN.csv", row.names = FALSE)
write.csv(DNH, file = "~/Post-doc/Data/Conditions Level Data/DNH.csv", row.names = FALSE)
write.csv(DNM, file = "~/Post-doc/Data/Conditions Level Data/DNM.csv", row.names = FALSE)
write.csv(DNN, file = "~/Post-doc/Data/Conditions Level Data/DNN.csv", row.names = FALSE)

#### Light conditions save files

write.csv(LNN, file = "~/Post-doc/Data/Conditions Level Data/LNN.csv", row.names = FALSE)
write.csv(LNL, file = "~/Post-doc/Data/Conditions Level Data/LNL.csv", row.names = FALSE)
write.csv(LNM, file = "~/Post-doc/Data/Conditions Level Data/LNM.csv", row.names = FALSE)
write.csv(LNH, file = "~/Post-doc/Data/Conditions Level Data/LNH.csv", row.names = FALSE)
write.csv(LNG, file = "~/Post-doc/Data/Conditions Level Data/LNG.csv", row.names = FALSE)

write.csv(LLN, file = "~/Post-doc/Data/Conditions Level Data/LLN.csv", row.names = FALSE)
write.csv(LLL, file = "~/Post-doc/Data/Conditions Level Data/LLL.csv", row.names = FALSE)
write.csv(LLM, file = "~/Post-doc/Data/Conditions Level Data/LLM.csv", row.names = FALSE)
write.csv(LLG, file = "~/Post-doc/Data/Conditions Level Data/LLG.csv", row.names = FALSE)


write.csv(LMN, file = "~/Post-doc/Data/Conditions Level Data/LMN.csv", row.names = FALSE)
write.csv(LMG, file = "~/Post-doc/Data/Conditions Level Data/LMG.csv", row.names = FALSE)


write.csv(LHN, file = "~/Post-doc/Data/Conditions Level Data/LHN.csv", row.names = FALSE)


write.csv(LEN, file = "~/Post-doc/Data/Conditions Level Data/LEN.csv", row.names = FALSE)


```





