---
title: "Parameterization Model"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
This analysis extracts swimming parameters from each of the 127 different experimental conditions tested. Then a random forest model is built and saved so that someone downstream can pull the full set of parameters (or whatever they need) given an arbitrary set of environmental conditions.

The experimental conditons are: flow rate, chlorophyll concentration, guano presence, and light presence.

The swimming parameters are: 
 - Mean velocity magnitude
 - Velocity magnitude variance
 - Velocity magnitude autocorrelation slope, intercept, residual
 - Velocity magnitude bimodal test significance
 - Mean angle (horizontal/vertical)… plus same relative to flow direction
 - Angle coefficient of dispersion (horizontal/vertical) … plus same relative to flow direction
 - Heading (horizontal) autocorrelation slope, intercept, residual
 - ... (there will be more)

```{r echo=FALSE}
library(ggplot2)
library(GGally)
library(hexbin)
library(diptest)
library(tidymodels)
library(randomForest)
library('matrixStats')

source('../functions/parameters-source.R')

#load("~/Post-doc/Data/Total Merged Data File (Oct 5 2023).RData")
load('~/Work/Data/Antarctic/CC.TotalData.2023.09.20.RData')  # loads the most recent version of the data, after it has been cleaned, processed and transformed into a singular dataframe, that has then been saved as a .Rdata file.
CC.TotalData$Chlorophyll <- as.numeric(as.character(CC.TotalData$Chlorophyll))  
CC.TotalData$Light <- as.numeric((CC.TotalData$Light)) - 1  
CC.TotalData$Guano <- as.numeric((CC.TotalData$Guano)) - 1  
CC.TotalData$Flow.rate <- as.numeric(as.character(CC.TotalData$Flow.rate))  
```

The experimental conditions tested were:
 - Flow rates: 0, 0.6, 3.0, 5.9, 8.9
 - Chlorophyll concentrations: 0.00, 1.01, 2.70, 2.80, 3.00, 3.70, 4.30, 4.50, 4.60, 5.50, 5.70, 5.90, 6.00, 6.10, 7.60, 9.00, 13.50, 16.00, 16.90, 19.00
 - Guano presence: absent, present
 - Light presence: absent, present
Of the possible combinations, 127 combinations were tested in an experimental setting.

```{r echo=FALSE}
conditions <- getconditions(CC.TotalData) # A matrix of all combinations of experimental conditions, with columns = flow rate, chlorophyll conc., guano, light
conditions <- setNames(conditions,c(
  "flow.rate","chlorophyll","guano","light"))
```

Now we need to extract all of the swimming parameters for each experiment.

```{r echo=F}
param.names <- NA
parameters <- matrix(NA, nrow = dim(conditions)[1], ncol = 21)

for (i in 1:dim(conditions)[1])  
{
  velocity <- CC.TotalData$smooth.v[
  (CC.TotalData$Flow.rate==conditions[i,1] &
     CC.TotalData$Chlorophyll==conditions[i,2] &
     as.numeric(CC.TotalData$Guano)==conditions[i,3] &
     as.numeric(CC.TotalData$Light)==conditions[i,4])]
  # Check whether combination was run as an experiment
  # ...and if not, set parameters to NA
  if (length(velocity) <= 1 | length(velocity[!is.na(velocity)])==0) {
    parameters[i,] <- NA } else {
      
      # Pull and bin velocity and heading time series for selcted experiment
      idx <- 1:length(velocity)
      bx <- seq(from=0.5, to=length(velocity), by=30)
      velocity <- binMeans(y = velocity, x = idx, bx = bx)
      heading.h <- CC.TotalData$smooth.h.heading[
        (CC.TotalData$Flow.rate==conditions[i,1] & 
          CC.TotalData$Chlorophyll==conditions[i,2] & 
          as.numeric(CC.TotalData$Guano)==conditions[i,3] &
          as.numeric(CC.TotalData$Light)==conditions[i,4])]
      heading.h <- binMeans(y=heading.h, x = idx, bx = bx)
      heading.v <- CC.TotalData$smooth.v.heading[
        (CC.TotalData$Flow.rate==conditions[i,1] & 
          CC.TotalData$Chlorophyll==conditions[i,2] & 
          as.numeric(CC.TotalData$Guano)==conditions[i,3] &
          as.numeric(CC.TotalData$Light)==conditions[i,4])]
      heading.v <- binMeans(y= heading.v, x = idx, bx = bx)
      
      # Add parameters one by one
      
      # Parameters for velocity magnitude
      ip <- 1
      param.names[ip] <- 'velocity mean'
      parameters[i,ip] <- mean(velocity)

      ip <- ip+1
      param.names[ip] <- 'velocity st.dev.'
      parameters[i,ip] <- sd(velocity)

      params.out <- getautocorrparams(log10(velocity))
      ip <- ip+1
      param.names[ip] <- 'velocity autocorr slope'
      parameters[i,ip] <- params.out$slope
      ip <- ip+1
      param.names[ip] <- 'velocity autocorr intercept'
      parameters[i,ip] <- params.out$intercept
      ip <- ip+1
      param.names[ip] <- 'velocity autocorr residuals'
      parameters[i,ip] <- params.out$resid
      ip <- ip+1
      param.names[ip] <- 'velocity autocorr coefficient (rho)'
      parameters[i,ip] <- params.out$rho
      ip <- ip+1
      param.names[ip] <- 'velocity dip test (p-value)'
      parameters[i,ip] <- params.out$dip

      # Parameters for heading.h
      ip <- ip+1
      param.names[ip] <- 'heading.h mean'
      parameters[i,ip] <- mean(heading.h)

      ip <- ip+1
      param.names[ip] <- 'heading.h st.dev.'
      parameters[i,ip] <- sd(heading.h)

      params.out <- getautocorrparams(heading.h)
      ip <- ip+1
      param.names[ip] <- 'heading.h autocorr slope'
      parameters[i,ip] <- params.out$slope
      ip <- ip+1
      param.names[ip] <- 'heading.h autocorr intercept'
      parameters[i,ip] <- params.out$intercept
      ip <- ip+1
      param.names[ip] <- 'heading.h autocorr residuals'
      parameters[i,ip] <- params.out$resid
      ip <- ip+1
      param.names[ip] <- 'heading.h autocorr coefficient (rho)'
      parameters[i,ip] <- params.out$rho
      ip <- ip+1
      param.names[ip] <- 'heading.h dip test (p-value)'
      parameters[i,ip] <- params.out$dip

      # Parameters for heading.v
      ip <- ip+1
      param.names[ip] <- 'heading.v mean'
      parameters[i,ip] <- mean(heading.v)

      ip <- ip+1
      param.names[ip] <- 'heading.v st.dev.'
      parameters[i,ip] <- sd(heading.v)

      params.out <- getautocorrparams(heading.v)
      ip <- ip+1
      param.names[ip] <- 'heading.v autocorr slope'
      parameters[i,ip] <- params.out$slope
      ip <- ip+1
      param.names[ip] <- 'heading.v autocorr intercept'
      parameters[i,ip] <- params.out$intercept
      ip <- ip+1
      param.names[ip] <- 'heading.v autocorr residuals'
      parameters[i,ip] <- params.out$resid
      ip <- ip+1
      param.names[ip] <- 'heading.v autocorr coefficient (rho)'
      parameters[i,ip] <- params.out$rho
      ip <- ip+1
      param.names[ip] <- 'heading.v dip test (p-value)'
      parameters[i,ip] <- params.out$dip


  }  
}

colnames(parameters) <- param.names

```

